### 2016-06-29 GPCE2016/sections/RelatedWork.tex
preparing for GPCE
Revised Section 4

\paragraph{Models of \objectoriented programming}
There are traditionally two big styles of OOP: \classbased and
\prototypebased. The \classbased tradition started with Simula~\cite{Dahl66simula},
and is the dominant style of OOP today. Major languages such
as Java, C\#, C++ or Scala favour a \classbased OOP style. Very often
\classbased languages are statically typed and they have interfaces or
some other similar mechanisms such as traits. However, in contrast to
IB, interfaces or traits in CB are not meant to
replace classes, but rather, they complement classes. Normally
interfaces or traits define the signatures of the methods and
\emph{may} have some behaviour (such as in Java 8 interfaces or Scala
traits). However classes are still responsible for object
instantiation and handling state. \Prototypebased languages started
with Self~\cite{Ungar87self} and are still widely used today via languages like
JavaScript. Frequently \prototypebased languages are dynamically
typed. IB is clearly closer to CB. However the
key difference is that classes are not needed in IB. Object interfaces recover the responsibility of object
instantiation, and abstract state operations provide a way to deal
with state. A primary motivation of IB is to improve
modularity and flexibility. Central to these goals are the
more expressive and automated forms of type-refinement, and support
for multiple interface inheritance.

@@

>>>>

\begin{comment}
\paragraph{Models of \objectoriented programming}
There are traditionally two big styles of OOP: \classbased and
\prototypebased. The \classbased tradition started with Simula~\cite{Dahl66simula},
and is the dominant style of OOP today. Major languages such
as Java, C\#, C++ or Scala favour a \classbased OOP style. Very often
\classbased languages are statically typed and they have interfaces or
some other similar mechanisms such as traits. However, in contrast to
IB, interfaces or traits in CB are not meant to
replace classes, but rather, they complement classes. Normally
interfaces or traits define the signatures of the methods and
\emph{may} have some behaviour (such as in Java 8 interfaces or Scala
traits). However classes are still responsible for object
instantiation and handling state. \Prototypebased languages started
with Self~\cite{Ungar87self} and are still widely used today via languages like
JavaScript. Frequently \prototypebased languages are dynamically
typed. IB is clearly closer to CB. However the
key difference is that classes are not needed in IB. Object interfaces recover the responsibility of object
instantiation, and abstract state operations provide a way to deal
with state. A primary motivation of IB is to improve
modularity and flexibility. Central to these goals are the
more expressive and automated forms of type-refinement, and support
for multiple interface inheritance.
\end{comment}

@@

\paragraph{Automatically generated Getters and Setters}
\bruno{Need to discuss automatic generation of setter and
  getters, and then discuss this text about injections. See reviews
  and reply.}
By declaring fields in Newspeak and other languages,
the programmers specifies field signatures and (critically) the intention of storing such information. 
Then the language generates getters and setters.
Once state is abstracted away, it is well known that state
access can be replaced with computation, but the type of the field stays the same.
% Our fluid approach to state is specular:
In our approach,
the intention of storing the information is not expressed by the programmer and set in stone, 
but can vary by inheritance: we generate the idea of the field
just starting from signatures of getters and setters.
In this case, we leverage on our fluid state to changing the underling type of the field,
 and our \Q@with@ provides the right injection from the old type to the new.
